Collective sheet:

## Binominal:

```{r}
numberOfItems <- 2
success <- 0
prob <- 0.5

#Calculate the probability of x sucsess, when pulling n numberOfItems
#where the probability of sucsess is prob.

#Beregn sandsynligheden for x succeser, når der vælges n antal ting
#Og sandsynligheden for en succses er prob.

pbinom(success,numberOfItems,prob)
```

## Hyper

Probability

```{r}
Type1Drawn <- 1
Type1All <- 2
Type2All <- 2
AllDrawn <- 2

#The probability of having drawn x Type1Drawn, in a draw of n AllDrawn.
#Where there are x of Type1All and x of Type2All to choose from.

dhyper(x=Type1Drawn, m=Type1All, n=Type2All, k=AllDrawn)

```

Variance

```{r}

#Calculate the variance given a probability (p) and number of participants (n)
n <- 25
p <- 0.8

#variance
n*p*(1-p)

```

## Poisson

## Chi Squared
```{r}

?chisq.test
?qchisq

```


## One way Anova

## Two way Anova

## Exponential

## Normal

## Confidence interval

Mean

```{r}
lower <- 2.26
upper <- 5.26
  
#Calculate the mean from a lower and an upper bound of a confidence interval of the mean
(lower+upper)/2
#Note you cannot know the sample mean from simulated data

```

Calculate confidence interval

```{r}
n <- 10
mean <- 0
sd <- 0
standardError <- 945.5

#Calculate qt
numberOfItems <- 2
degreeFreedom <- n-numberOfItems
qt <- qt(0.975,degreeFreedom)
qt
#confidence interval
mean + c(-1,1)* qt * sd/sqrt(n)
mean + c(-1,1)* qt * standardError


#Given qt 
qt <- 0

mean + c(-1,1)* qt * sd/sqrt(n)
mean + c(-1,1)* qt * standardError

```

## Linear Simulation

Variance

```{r}
#Simulate to get variance, normal distribution
#given 2*Y + 2*X + 4

k <- 800000

MeanX <- 10
SdX <- sqrt(4)

MeanY <- 20
SdY <- sqrt(25)

X <- rnorm(k,MeanX,SdX)
Y <- rnorm(k,MeanY,SdY)

z <- 2* Y + 2*X +4

var(z)
```

Standard Divination

```{r}
#Simulate to get Standard Divination, normal distribution
#given 2*Y^2 + X^3/3

k <- 800000

MeanX <- 10
SdX <- sqrt(4)

MeanY <- 20
SdY <- sqrt(25)

X <- rnorm(k,MeanX,SdX)
Y <- rnorm(k,MeanY,SdY)

z <- 2*Y^2 + X^3/3

sd(z)
```

## test statistic

Calculate tobs

```{r}
#Given n number of samples
#Given the actual mean or something similar
#Compared to the expected mean or something similar

n <- 20
actual <- 0
expected <- 0

# given standard deviation
sd <- -1
#beregn t_obs (tobs)
(actual - expected)/(sd/sqrt(n))



# given standard error
standardError <- 5.867*10^4
#beregn t_obs (tobs)
(actual - expected)/(standardError)
```

tobs on a certain p-value

```{r}
NumberOfSamples <- 20
degreeFreedom <- NumberOfSamples-1
pValue <- 0.001

qt(1-pValue/2,degreeFreedom)
qt(pValue/2,degreeFreedom)




```

## Linear Model:

I en linear model af

```{r}
lm(X ~ Y)
```

Gælder det at: X er dependent variable Y er explanatory variable

Beta_0 er (Intecept) estimate Beta_1 er Y estimate sigma er residual standard error.

Predictions ved x_0 udregnes som:

```{r}
sxx <- (n-1) * var(Y)
t_alpha <- qt(0.95, df=n-2) #alpha = 0.9
beta_0 + beta_1 * x_0 + c(-1,1) * t_alpha * res_err * sqrt(1+1/n + (x_0-mean(x)/ sxx))
```
